---
title: "Quick test mass calculator report"
date: "`r format(Sys.time(), ' %a %X, %d %B %Y')`"
output: pdf_document
params:
  Soil_N_supply: NA
  p_N_supply: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


## Nitrogen staus in soil

```{r}
knitr::kable(params$Soil_N_supply, caption = "Soil nitrogen supply.")
```



## Graph


```{r, fig.height=6, fig.width=10, dpi=300}
params$p_N_supply
```

## Acknowledgement 

The aim of the MPI SFF project Nitrogen – Measure it and Manage it was to develop a nitrate quick test management tool to assist with N fertiliser decisions for arable and vegetable crops.

MPI’s Sustainable Farming Fund was the main funder for the three year programme of work, with co-funding and in-kind support from; FAR, HortNZ’s VR&I Board, Waikato Regional Council, Ravensdown, Ballance Agri-Nutrients, Hawke’s Bay Regional Council and Potatoes NZ.

The collaborating research organisation delivering the science programme was   
Plant & Food Research.

Shiny application developer:  
Jian Liu, Plant & Food Research  

Contributors:   
Diana Mathers, Foundation for Arable Research   
Steven Dellow, Plant & Food Research   
Hymmi Kong, Plant & Food Research   
Matthew Norris, Waikato Regional Council   
Adrian Hunt, Hort Innovation   

Source code is avaiable on GitHub <https://github.com/frank0434/QuickTestMassBalanceCalculator>


<p>Disclaimer</p>

This report is copyright to the Foundation for Arable Research (FAR) and may not be reproduced or copied
in any form whatsoever without FAR’s written permission. The report is intended to provide accurate and
adequate information relating to the subject matters contained in it and is based on information current at the time of
report. Information contained in this report is general in nature and not intended as a substitute for specific
professional advice on any matter and should not be relied upon for that purpose. It has been prepared and made
available to all persons and entities strictly on the basis that FAR, its researchers and authors are fully excluded from
any liability for damages arising out of any reliance in part or in full upon any of the information for any purpose.
