---
title: "Quick test mass calculator report"
date: "`r format(Sys.time(), ' %a %X, %d %B %Y')`"
output: pdf_document
params:
  crop_info: NA
  Soil_N_supply: NA
  p_N_uptake: NA
  p_N_supply: NA
  tab_NCrop: NA
  tab_N_requirements: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Crop information



```{r}
knitr::kable(params$crop_info, caption = "Information about the crop")
```

## Nitrogen staus in soil

```{r}
knitr::kable(params$Soil_N_supply, caption = "Soil nitrogen supply.")
```

## Estimated Crop Nitrogen Uptake with Remaining Crop Nitrogen Requirement

```{r}
knitr::kable(params$tab_N_requirements, caption = "Soil nitrogen supply.")
```


## Nitrogen requirement to Next Sampling Date 

```{r}
knitr::kable(params$tab_N_requirements, caption = "Soil nitrogen supply.")
```


## Graph

```{r, fig.height=12, fig.width=10, dpi=300}
library(cowplot)

plot_grid(params$p_N_supply, params$p_N_uptake,  align = "v", ncol = 1)
# +  theme(legend.position = c(0.15, 0.8))
```


## Acknowledgement 

Funded by [FAR](https://www.far.org.nz/)

Projected was leaded by MATTHEW NORRIS.

Matthew also developed the original excel tool which is free to download on the FAR website. 


The app is a remake by [Jian Liu](https://www.linkedin.com/in/jian-aka-frank-liu-9623379a/) from [Plant and Food Research](https://www.plantandfood.co.nz/)

Code is avaiable on [GitHub](https://github.com/PlantandFoodResearch/QuickTestMassBalanceCalculator)

